---
title: "Big Data Challenge 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

How GDP, health expenditure, education, life expectancy impact the prevalencedrug users per country

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# echo=FALSE will stop the code chunk from appearing in the knit document
# warning=FALSE and message=FALSE will stop R messages from appearing in the knit document
library(tidyverse)
library(dbplyr)
#library(expss)
library(ggplot2)
path <- "https://raw.githubusercontent.com/ntaback/UofT_STA130/master/Fall2018/Finalproject/"

democracyindex2017 <- read_csv(paste0(path,"democracyindex2017.csv"))
education_cia2017 <- read_csv(paste0(path,"education_cia2017.csv"))
gdpppp_cia2017 <- read_csv(paste0(path,"gdpppp_cia2017.csv"))
lifeexpect_cia2017 <- read_csv(paste0(path,"lifeexpect_cia2017.csv"))
healthexpend_cia2017 <- read_csv(paste0(path,"healthexpend_cia2017.csv"))
internetusers_cia2017 <- read_csv(paste0(path,"internetusers_cia2017.csv"))
telephonelines_cia2017 <- read_csv(paste0(path,"telephonelines_cia2017.csv"))
population_cia2017 <- read_csv(paste0(path,"population_cia2017.csv"))
world_regions <- read_csv(paste0(path,"world_regions.csv"))
prevalence_cannabis_use <- read.csv("C:\\Users\\anhmi\\Documents\\data o C\\Documents\\Anh Minh Nguyen\\Self-study\\Big Data Challenge 2019\\My data\\Sheet_1_data.csv", header = TRUE) #change the path to your file path 
```

## Filter by regions

From the World Regions file, create different table for different regions

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Europe <- filter(world_regions, Region == "Europe")
Africa <- filter(world_regions, Region == "Africa")
North_America <- filter(world_regions, Region == "North America")
Arab <- filter(world_regions, Region == "Arab States")
Asia <- filter(world_regions, Region == "Asia & Pacific")
South_America <- filter(world_regions, Region == "South/Latin America")

```



## The average GDP for each regions
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Find the Average GDP for each regions, then create a table with all new average GDP just found 
new_GDP_table <-gdpppp_cia2017%>%group_by(Country)%>%summarise(GDP_per_capita = as.numeric(gsub("[\\$,]","",`GDP - PER CAPITA (PPP)`))) #change the GDP column from character to number

Europe_join_GDP <- inner_join(x = Europe, y = new_GDP_table,by = 'Country')
Europe_Total_GDP <- Europe_join_GDP%>%select(GDP_per_capita)%>%sum()
Europe_average_GDP <- Europe_Total_GDP/as.numeric(count(Europe_join_GDP))

Africa_join_GDP <- inner_join(x = Africa, y =new_GDP_table,by = 'Country')
Africa_Total_GDP <- Africa_join_GDP%>%select(GDP_per_capita)%>%sum()
Africa_average_GDP <- Africa_Total_GDP/as.numeric(count(Africa_join_GDP))


North_America_join_GDP <- inner_join(x = North_America, y = new_GDP_table,by = 'Country')
North_America_Total_GDP <- North_America_join_GDP%>%select(GDP_per_capita)%>%sum()
North_America_average_GDP <- North_America_Total_GDP/as.numeric(count(North_America_join_GDP))


Arab_join_GDP <- inner_join(x = Arab, y =new_GDP_table,by = 'Country')
Arab_Total_GDP <- Arab_join_GDP%>%select(GDP_per_capita)%>%sum()
Arab_average_GDP <- Arab_Total_GDP/as.numeric(count(Arab_join_GDP))


Asia_join_GDP <- inner_join(x = Asia, y =new_GDP_table,by = 'Country')
Asia_Total_GDP <- Asia_join_GDP%>%select(GDP_per_capita)%>%sum()
Asia_average_GDP <- Asia_Total_GDP/as.numeric(count(Asia_join_GDP))


South_America_join_GDP <- inner_join(x = South_America, y =new_GDP_table,by = 'Country')
South_America_Total_GDP <- South_America_join_GDP%>%select(GDP_per_capita)%>%sum()
South_America_average_GDP <- South_America_Total_GDP/as.numeric(count(South_America_join_GDP))


#Average_GDP_table <- matrix(c(Europe_average_GDP, Africa_average_GDP, North_America_average_GDP, #Arab_average_GDP, Asia_average_GDP, South_America_average_GDP), ncol = 6)
#rownames(Average_GDP_table) <- c("Average_GDP")
#colnames(Average_GDP_table) <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
#Average_GDP_table1 <-data.frame(Average_GDP_table)
#Average_GDP_table1["Europe"]
region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_GDP <-  c(Europe_average_GDP, Africa_average_GDP, North_America_average_GDP, Arab_average_GDP, Asia_average_GDP, South_America_average_GDP)
Average_GDP_table <- data.frame(region_name, region_GDP, stringsAsFactors = FALSE)
Average_GDP_table



```

##The average democracy score by each region 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
Europe_democracy_relat <- inner_join(x = democracyindex2017, y = Europe, by = "Country") 
Europe_democracy_table <- Europe_democracy_relat %>% group_by(Country)%>% summarise(demo_score = as.numeric(Score))
Europe_total_demo <- Europe_democracy_table%>%select(demo_score)%>%sum()
Europe_average_demo <- Europe_total_demo/as.numeric(count(Europe_democracy_table))

Africa_democracy_relat <- inner_join(x = democracyindex2017, y = Africa, by = "Country") 
Africa_democracy_table <- Africa_democracy_relat %>% group_by(Country)%>% summarise(demo_score = as.numeric(Score))
Africa_total_demo <- Africa_democracy_table%>%select(demo_score)%>%sum()
Africa_average_demo <- Africa_total_demo/as.numeric(count(Africa_democracy_table))

North_America_democracy_relat <- inner_join(x = democracyindex2017, y = North_America, by = "Country") 
North_America_democracy_table <- North_America_democracy_relat %>% group_by(Country)%>% summarise(demo_score = as.numeric(Score))
North_America_total_demo <- North_America_democracy_table%>%select(demo_score)%>%sum()
North_America_average_demo <- North_America_total_demo/as.numeric(count(North_America_democracy_table))

South_America_democracy_relat <- inner_join(x = democracyindex2017, y = South_America, by = "Country") 
South_America_democracy_table <- South_America_democracy_relat %>% group_by(Country)%>% summarise(demo_score = as.numeric(Score))
South_America_total_demo <- South_America_democracy_table%>%select(demo_score)%>%sum()
South_America_average_demo <- South_America_total_demo/as.numeric(count(South_America_democracy_table))

Arab_democracy_relat <- inner_join(x = democracyindex2017, y = Arab, by = "Country") 
Arab_democracy_table <- Arab_democracy_relat %>% group_by(Country)%>% summarise(demo_score = as.numeric(Score))
Arab_total_demo <- Arab_democracy_table%>%select(demo_score)%>%sum()
Arab_average_demo <- Arab_total_demo/as.numeric(count(Arab_democracy_table))

Asia_democracy_relat <- inner_join(x = democracyindex2017, y = Asia, by = "Country") 
Asia_democracy_table <- Asia_democracy_relat %>% group_by(Country)%>% summarise(demo_score = as.numeric(Score))
Asia_total_demo <- Asia_democracy_table%>%select(demo_score)%>%sum()
Asia_average_demo <- Asia_total_demo/as.numeric(count(Asia_democracy_table))
#new_democracy_table <- democracyindex2017 %>% group_by(Country)%>%summarise(demo_score = as.numeric(Score)) #change the GDP column from character to number

region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_demo <-  c(Europe_average_demo, Africa_average_demo, North_America_average_demo, Arab_average_demo, Asia_average_demo, South_America_average_demo)
Average_demo_table <- data.frame(region_name, region_demo, stringsAsFactors = FALSE)
Average_demo_table
```

## The average population by region 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
Europe_population <- inner_join(x = population_cia2017, y = Europe, by = "Country")
Europe_total_population <- Europe_population%>%select(POPULATION)%>%sum()
Europe_average_population <- Europe_total_population/as.numeric(count(Europe_population))

Africa_population <- inner_join(x = population_cia2017, y = Africa, by = "Country")
Africa_total_population <- Africa_population%>%select(POPULATION)%>%sum()
Africa_average_population <- Africa_total_population/as.numeric(count(Africa_population))

North_America_population <- inner_join(x = population_cia2017, y = North_America, by = "Country")
North_America_total_population <- North_America_population%>%select(POPULATION)%>%sum()
North_America_average_population <- North_America_total_population/as.numeric(count(North_America_population))

South_America_population <- inner_join(x = population_cia2017, y = South_America, by = "Country")
South_America_total_population <- South_America_population%>%select(POPULATION)%>%sum()
South_America_average_population <- South_America_total_population/as.numeric(count(South_America_population))

Arab_population <- inner_join(x = population_cia2017, y = Arab, by = "Country")
Arab_total_population <- Arab_population%>%select(POPULATION)%>%sum()
Arab_average_population <- Arab_total_population/as.numeric(count(Arab_population))

Asia_population <- inner_join(x = population_cia2017, y = Asia, by = "Country")
Asia_total_population <- Asia_population%>%select(POPULATION)%>%sum()
Asia_average_population <- Asia_total_population/as.numeric(count(Asia_population))

region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_population <-  c(Europe_average_population, Africa_average_population, North_America_average_population, Arab_average_population, Asia_average_population, South_America_average_population)
Average_population_table <- data.frame(region_name, region_population, stringsAsFactors = FALSE)
Average_population_table
```

## The average life expectancy for each region 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Find the Average Life Expectancy for each regions, then create a table with all new average life expectancy just found 
LE_table <- lifeexpect_cia2017%>%group_by(Country)%>%summarise(LE_per_capita = as.numeric(gsub("[\\$,]","",`(YEARS)`))) #change the LE column from character to number

Europe_join_LE <- inner_join(x = Europe, y = LE_table,by = 'Country')
Europe_Total_LE <- Europe_join_LE%>%select(LE_per_capita)%>%sum()
Europe_average_LE <- Europe_Total_LE/as.numeric(count(Europe_join_LE))

Africa_join_LE <- inner_join(x = Africa, y =LE_table,by = 'Country')
Africa_Total_LE <- Africa_join_LE%>%select(LE_per_capita)%>%sum()
Africa_average_LE <- Africa_Total_LE/as.numeric(count(Africa_join_LE))


North_America_join_LE <- inner_join(x = North_America, y = LE_table,by = 'Country')
North_America_Total_LE <- North_America_join_LE%>%select(LE_per_capita)%>%sum()
North_America_average_LE <- North_America_Total_LE/as.numeric(count(North_America_join_LE))


Arab_join_LE <- inner_join(x = Arab, y =LE_table,by = 'Country')
Arab_Total_LE <- Arab_join_LE%>%select(LE_per_capita)%>%sum()
Arab_average_LE <- Arab_Total_LE/as.numeric(count(Arab_join_LE))


Asia_join_LE <- inner_join(x = Asia, y =LE_table,by = 'Country')
Asia_Total_LE <- Asia_join_LE%>%select(LE_per_capita)%>%sum()
Asia_average_LE <- Asia_Total_LE/as.numeric(count(Asia_join_LE))


South_America_join_LE <- inner_join(x = South_America, y =LE_table,by = 'Country')
South_America_Total_LE <- South_America_join_LE%>%select(LE_per_capita)%>%sum()
South_America_average_LE <- South_America_Total_LE/as.numeric(count(South_America_join_LE))


region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_life_expectancy <-  c(Europe_average_LE, Africa_average_LE, North_America_average_LE, Arab_average_LE, Asia_average_LE, South_America_average_LE)
Average_LE_table <- data.frame(region_name, region_life_expectancy, stringsAsFactors = FALSE)
Average_LE_table

```

## The average Internet Users in each region 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Find the Average Internet Users for each regions, then create a table with all new average internet users just found 
IU_table <- internetusers_cia2017%>%group_by(Country)%>%summarise(IU_per_capita = as.numeric(gsub("[\\$,]","",`INTERNET USERS`))) #change the IU column from character to number

Europe_join_IU <- inner_join(x = Europe, y = IU_table,by = 'Country')
Europe_Total_IU <- Europe_join_IU%>%select(IU_per_capita)%>%sum()
Europe_average_IU <- Europe_Total_IU/as.numeric(count(Europe_join_IU))

Africa_join_IU <- inner_join(x = Africa, y =IU_table,by = 'Country')
Africa_Total_IU <- Africa_join_IU%>%select(IU_per_capita)%>%sum()
Africa_average_IU <- Africa_Total_IU/as.numeric(count(Africa_join_IU))


North_America_join_IU <- inner_join(x = North_America, y = IU_table,by = 'Country')
North_America_Total_IU <- North_America_join_IU%>%select(IU_per_capita)%>%sum()
North_America_average_IU <- North_America_Total_IU/as.numeric(count(North_America_join_IU))


Arab_join_IU <- inner_join(x = Arab, y =IU_table,by = 'Country')
Arab_Total_IU <- Arab_join_IU%>%select(IU_per_capita)%>%sum()
Arab_average_IU <- Arab_Total_IU/as.numeric(count(Arab_join_IU))


Asia_join_IU <- inner_join(x = Asia, y =IU_table,by = 'Country')
Asia_Total_IU <- Asia_join_IU%>%select(IU_per_capita)%>%sum()
Asia_average_IU <- Asia_Total_IU/as.numeric(count(Asia_join_IU))


South_America_join_IU <- inner_join(x = South_America, y =IU_table,by = 'Country')
South_America_Total_IU <- South_America_join_IU%>%select(IU_per_capita)%>%sum()
South_America_average_IU <- South_America_Total_IU/as.numeric(count(South_America_join_IU))


region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_internet_users <-  c(Europe_average_IU, Africa_average_IU, North_America_average_IU, Arab_average_IU, Asia_average_IU, South_America_average_IU)
Average_IU_table <- data.frame(region_name, region_internet_users, stringsAsFactors = FALSE)
Average_IU_table
```

## The average education expenditure (based on % of GDP) in each region

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# delete the 'Rank' and 'Date of Information' column in table education_cia2017
education_cia20171 <- education_cia2017 %>% select(-starts_with("Rank"))
new_edu_table <- education_cia20171 %>% select(-starts_with("Date"))

Europe_join_edu <- inner_join(x = Europe, y = new_edu_table, by = 'Country')
Europe_Total_edu <- Europe_join_edu%>%select(4)%>%sum()
Europe_average_edu <- Europe_Total_edu/as.numeric(count(Europe_join_edu))

Africa_join_edu <- inner_join(x = Africa, y = new_edu_table, by = 'Country')
Africa_Total_edu <- Africa_join_edu%>%select(4)%>%sum()
Africa_average_edu <- Africa_Total_edu/as.numeric(count(Africa_join_edu))

North_America_join_edu <- inner_join(x = North_America, y = new_edu_table, by = 'Country')
North_America_Total_edu <- North_America_join_edu%>%select(4)%>%sum()
North_America_average_edu <- North_America_Total_edu/as.numeric(count(North_America_join_edu))

Arab_join_edu <- inner_join(x = Arab_States, y = new_edu_table, by = 'Country')
Arab_Total_edu <- Arab_join_edu%>%select(4)%>%sum()
Arab_average_edu <- Arab_Total_edu/as.numeric(count(Arab_join_edu))

Asia_join_edu <- inner_join(x = Asia_Pacific, y = new_edu_table, by = 'Country')
Asia_Total_edu <- Asia_join_edu%>%select(4)%>%sum()
Asia_average_edu <- Asia_Total_edu/as.numeric(count(Asia_join_edu))

South_America_join_edu <- inner_join(x = South_America, y = new_edu_table, by = 'Country')
South_America_Total_edu <- South_America_join_edu%>%select(4)%>%sum()
South_America_average_edu <- South_America_Total_edu/as.numeric(count(South_America_join_edu))

region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_edu <-  c(Europe_average_edu, Africa_average_edu, North_America_average_edu, Arab_average_edu, Asia_average_edu, South_America_average_edu)
Average_edu_table <- data.frame(region_name, region_edu, stringsAsFactors = FALSE)
Average_edu_table
```

## The average of health expenditure (based on % of GDP) in each region 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
# delete "Rank" and the 'Date of Information' column in table lifeexpect_cia2017
healthexpend_cia20171 <- healthexpend_cia2017 %>% select(-starts_with("Rank"))
new_healthexpend_table <- healthexpend_cia20171 %>% select(-starts_with("Date"))

Europe_join_healthexpend <- inner_join(x = Europe, y = new_healthexpend_table, by = 'Country')
Europe_Total_healthexpend <- Europe_join_healthexpend%>%select(4)%>%sum()
Europe_average_healthexpend <- Europe_Total_healthexpend/as.numeric(count(Europe_join_healthexpend))

Africa_join_healthexpend <- inner_join(x = Africa, y = new_healthexpend_table, by = 'Country')
Africa_Total_healthexpend <- Africa_join_healthexpend%>%select(4)%>%sum()
Africa_average_healthexpend <- Africa_Total_healthexpend/as.numeric(count(Africa_join_healthexpend))

North_America_join_healthexpend <- inner_join(x = North_America, y = new_healthexpend_table, by = 'Country')
North_America_Total_healthexpend <- North_America_join_healthexpend%>%select(4)%>%sum()
North_America_average_healthexpend <- North_America_Total_healthexpend/as.numeric(count(North_America_join_healthexpend))

Arab_join_healthexpend <- inner_join(x = Arab_States, y = new_healthexpend_table, by = 'Country')
Arab_Total_healthexpend <- Arab_join_healthexpend%>%select(4)%>%sum()
Arab_average_healthexpend <- Arab_Total_healthexpend/as.numeric(count(Arab_join_healthexpend))

Asia_join_healthexpend <- inner_join(x = Asia_Pacific, y = new_healthexpend_table, by = 'Country')
Asia_Total_healthexpend <- Asia_join_healthexpend%>%select(4)%>%sum()
Asia_average_healthexpend <- Asia_Total_healthexpend/as.numeric(count(Asia_join_healthexpend))

South_America_join_healthexpend <- inner_join(x = South_America, y = new_healthexpend_table, by = 'Country')
South_America_Total_healthexpend <- South_America_join_healthexpend%>%select(4)%>%sum()
South_America_average_healthexpend <- South_America_Total_healthexpend/as.numeric(count(South_America_join_healthexpend))

region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_healthexpend <-  c(Europe_average_healthexpend, Africa_average_healthexpend, North_America_average_healthexpend, Arab_average_healthexpend, Asia_average_healthexpend, South_America_average_healthexpend)
Average_healthexpend_table <- data.frame(region_name, region_healthexpend, stringsAsFactors = FALSE)
Average_healthexpend_table
```


## Prevalence of cannabis in each region
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#1. Clean the prevalence data set, only pick the best measure names
clean_prevalence <- filter(prevalence_cannabis_use, Measure.Names == "Best")
clean_prevalence

Europe_prevalence <- inner_join(x = Europe, y = clean_prevalence)

Africa_prevalence <- inner_join(x = Africa, y = clean_prevalence)

North_America_prevalence <- inner_join(x = North_America, y = clean_prevalence)

South_America_prevalence <- inner_join(x = South_America, y = clean_prevalence)

Arab_prevalence <- inner_join(x = Arab, y = clean_prevalence)

Asia_prevalence <- inner_join(x = Asia, y = clean_prevalence)

Europe_prev_avg <- mean(Europe_prevalence$Measure.Values)
Africa_prev_avg <- mean(Africa_prevalence$Measure.Values)
NA_prev_avg <- mean(North_America_prevalence$Measure.Values)
SA_prev_avg <- mean(South_America_prevalence$Measure.Values)
Arab_prev_avg <- mean(Arab_prevalence$Measure.Values)
Asia_prev_avg <- mean(Asia_prevalence$Measure.Values)

region_name <- c("Europe", "Africa", "North_America", "Arab", "Asia", "South_America")
region_prev_age <-  c(Europe_prev_avg, Africa_prev_avg, NA_prev_avg, Arab_prev_avg, Asia_prev_avg, SA_prev_avg)
Average_prev_table <- data.frame(region_name, region_prev_age, stringsAsFactors = FALSE)
Average_prev_table

#create a table of prevalence cannabis 
#regression table 
#graph the relationship 

```

## Corelation between cannabis prevalence and GDP
```{r, echo=FALSE, message=FALSE, warning=FALSE}
#Average_prev_table ~ Average_GDP_table
GDP_cannabis<- inner_join(x = Average_prev_table, y = Average_GDP_table, by = "region_name")
GDP_cannabis
mod_GDP_cannabis <- lm(region_prev_age ~ region_GDP, data = GDP_cannabis)
mod_GDP_cannabis_summary <- summary(mod_GDP_cannabis)
mod_GDP_cannabis_summary$coefficients

#graph the plot
GDP_cannabis_plot <- GDP_cannabis %>%
 ggplot(aes(region_GDP, region_prev_age,)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and GDP of each world region ")
GDP_cannabis_plot

```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
demo_cannabis<- inner_join(x = Average_prev_table, y = Average_demo_table, by = "region_name")
demo_cannabis
mod_demo_cannabis <- lm(region_prev_age ~ region_demo, data = demo_cannabis)
mod_demo_cannabis_summary <- summary(mod_demo_cannabis)
mod_demo_cannabis_summary$coefficients

#graph the plot
demo_cannabis_plot <- demo_cannabis %>%
 ggplot(aes(region_demo, region_prev_age,)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and democracy of each world region ")
demo_cannabis_plot
```

## Correlation between cannabis use and population 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
population_cannabis<- inner_join(x = Average_prev_table, y = Average_population_table, by = "region_name")
population_cannabis
mod_population_cannabis <- lm(region_prev_age ~ region_population, data = population_cannabis)
mod_population_cannabis_summary <- summary(mod_population_cannabis)
mod_population_cannabis_summary$coefficients

#graph the plot
population_cannabis_plot <- population_cannabis %>%
 ggplot(aes(region_population, region_prev_age,)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and population of each world region ")
population_cannabis_plot

```

## Correlation between cannabis use and life expectancy 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
LE_cannabis<- inner_join(x = Average_prev_table, y = Average_LE_table, by = "region_name")
LE_cannabis
mod_LE_cannabis <- lm(region_prev_age ~ region_life_expectancy, data = LE_cannabis)
mod_LE_cannabis_summary <- summary(mod_LE_cannabis)
mod_LE_cannabis_summary$coefficients

#graph the plot
LE_cannabis_plot <- LE_cannabis %>%
 ggplot(aes(region_life_expectancy, region_prev_age,)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and life expectancy of each world region ")
LE_cannabis_plot
```

## Correlation between cannabis use and education
```{r, echo=FALSE, message=FALSE, warning=FALSE}
edu_cannabis<- inner_join(x = Average_prev_table, y = Average_edu_table, by = "region_name")
edu_cannabis
mod_edu_cannabis <- lm(region_prev_age ~ region_edu, data = edu_cannabis)
mod_edu_cannabis_summary <- summary(mod_edu_cannabis)
mod_edu_cannabis_summary$coefficients

#graph the plot
edu_cannabis_plot <- edu_cannabis %>%
 ggplot(aes(region_edu, region_prev_age,)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and education of each world region ")
edu_cannabis_plot

```

## Corelation between cannabis use and health expense 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
health_cannabis<- inner_join(x = Average_prev_table, y = Average_healthexpend_table, by = "region_name")
health_cannabis
mod_health_cannabis <- lm(region_prev_age ~ region_healthexpend, data = health_cannabis)
mod_health_cannabis_summary <- summary(mod_health_cannabis)
mod_health_cannabis_summary$coefficients

#graph the plot
health_cannabis_plot <- health_cannabis %>%
 ggplot(aes(region_healthexpend, region_prev_age)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and health expense of each world region ")
health_cannabis_plot

```

## Correlation between cannabis use and internet users
```{r, echo=FALSE, message=FALSE, warning=FALSE}
IU_cannabis<- inner_join(x = Average_prev_table, y = Average_IU_table, by = "region_name")
IU_cannabis
mod_IU_cannabis <- lm(region_prev_age ~ region_internet_users, data = IU_cannabis)
mod_IU_cannabis_summary <- summary(mod_IU_cannabis)
mod_IU_cannabis_summary$coefficients

#graph the plot
IU_cannabis_plot <- IU_cannabis %>%
 ggplot(aes(region_internet_users, region_prev_age)) +
 geom_point(aes(col = region_name)) +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and internet users of each world region ")
IU_cannabis_plot
```

## Correlation between cannabis use and GDP of all countries
```{r, echo=FALSE, message=FALSE, warning=FALSE}
all_GDP_cannabis <- inner_join(x = clean_prevalence, y = new_GDP_table, by = "Country")
all_GDP_cannabis <- all_GDP_cannabis%>%select(Country, GDP_per_capita, Measure.Values)
all_GDP_cannabis <- all_GDP_cannabis%>%rename(cannabis_prev = Measure.Values)
all_GDP_cannabis

mod_all_GDP_cannabis <- lm(cannabis_prev ~ GDP_per_capita, data = all_GDP_cannabis)
mod_all_GDP_cannabis_summary <- summary(mod_all_GDP_cannabis)
mod_all_GDP_cannabis_summary$coefficients

#graph the plot
all_GDP_cannabis_plot <- all_GDP_cannabis %>%
 ggplot(aes(GDP_per_capita, cannabis_prev)) +
 geom_point() +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between cannabis use and GDP in different countries")
all_GDP_cannabis_plot

```

## Correlation between cannabis use and population of all countries
```{r, echo=FALSE, message=FALSE, warning=FALSE}
all_pop_cannabis <- inner_join(x = clean_prevalence, y = population_cia2017, by = "Country")
all_pop_cannabis <- all_pop_cannabis%>%select(Country, POPULATION, Measure.Values)
all_pop_cannabis <- all_pop_cannabis%>%rename(cannabis_prev = Measure.Values)

mod_all_pop_cannabis <- lm(cannabis_prev ~ POPULATION, data = all_pop_cannabis)
mod_all_pop_cannabis_summary <- summary(mod_all_pop_cannabis)
mod_all_pop_cannabis_summary$coefficients

#graph the plot
all_pop_cannabis_plot <- all_pop_cannabis %>%
 ggplot(aes(POPULATION, cannabis_prev)) +
 geom_point() +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between prevalence of cannabis use and population in different countries")
all_pop_cannabis_plot


```

## Correlation between cannabis use and life expectancy 
```{r, echo=FALSE, message=FALSE, warning=FALSE}
all_LE_cannabis <- inner_join(x = clean_prevalence, y = lifeexpect_cia2017, by = "Country")
all_LE_cannabis <- all_LE_cannabis%>%select(Country, `(YEARS)`, Measure.Values)
all_LE_cannabis <- all_LE_cannabis%>%rename(cannabis_prev = Measure.Values, life_expect = `(YEARS)`)

mod_all_LE_cannabis <- lm(cannabis_prev ~ life_expect, data = all_LE_cannabis)
mod_all_LE_cannabis_summary <- summary(mod_all_LE_cannabis)
mod_all_LE_cannabis_summary$coefficients

#graph the plot
all_LE_cannabis_plot <- all_LE_cannabis %>%
 ggplot(aes(life_expect, cannabis_prev)) +
 geom_point() +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between prevalence of cannabis use and life expectancy in different countries")
all_LE_cannabis_plot
```

## Correlation between cannabis use and and health expenditure
```{r}
#not done yet 
all_HE_cannabis <- inner_join(x = clean_prevalence, y = new_healthexpend_table, by = "Country")
all_HE_cannabis <- all_HE_cannabis%>%select(Country, `(% OF GDP)`, Measure.Values)
all_HE_cannabis
all_LE_cannabis <- all_LE_cannabis%>%rename(cannabis_prev = Measure.Values, percent_of_GDP = `(% OF GDP)`)

mod_all_HE_cannabis <- lm(cannabis_prev ~ percent_of_GDP, data = all_HE_cannabis)
mod_all_HE_cannabis_summary <- summary(mod_all_HE_cannabis)
mod_all_HE_cannabis_summary$coefficients

#graph the plot
all_HE_cannabis_plot <- all_HE_cannabis %>%
 ggplot(aes(percent_of_GDP, cannabis_prev)) +
 geom_point() +
 theme_minimal()+
  geom_smooth(method="loess", se=F) +
  ggtitle("The relationship between prevalence of cannabis use and health expenditure in different countries")
all_HE_cannabis_plot
```


